On the presentation of orthogonal groups over polynomial rings

### 2019-05-18 dl-paper.tex
Proving one more lemma

Denote by $V$ the subset of $\St(\Phi, A[X, X^{-1}]) \times C \times (1 + M)^*$ consisting of those triples $(g, h \overline{G}^0_M, u)$ for which $\pi(g, h, u) = g \cdot j_-(h) \cdot \{ X, u \} \in \overline{G}_M^{\geq 0}$. The correctness of this definition is clear from the above commutative diagram.

The next step of the proof is to define for $\alpha \in \Phi$, $a \in A$ a  function $T_\alpha(aX^{-1}) \colon V \to V$. This function is defined for those triples $(g, h, u)$ for which $\pi(g, h, u) \in P_\alpha(*) \subseteq \overline{G}_M^{\geq 0}$. If $\pi(g, h, u) \in P_\alpha(m)$ for some $m \in M$, then $T_\alpha(aX^{-1})$ is defined via the following identity:
\[ T_\alpha(aX^{-1}) (g, h, u) = \left( x_\alpha(aX^{-1})\cdot g ,\
                                         h \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right),\ 
                                         u \cdot (1 + am)\right).\]
It is easy to verify that $\pi(T_\alpha(aX^{-1}) (g, h, u)) = S_\alpha(a, \pi(g, h, u)).$

>>>>

Denote by $V$ the subset of $\St(\Phi, A[X, X^{-1}]) \times G^{\leq 0} \times (1 + M)^*$ consisting of those triples $(g, h, u)$ for which 
$\pi(g, h, u) = g \cdot j_-(h) \cdot \{ X, u \} \in \overline{G}_M^{\geq 0}$.
Denote by $\overline{V}$ the image of $V$ in $\St(\Phi, A[X, X^{-1}]) \times C \times (1 + M)^*$
under the obvious map induced by the projection $G^{\leq 0} \to C$
 (of course, these triples still can be characterized by the property that $(g, h \overline{G}^0_M, u) \in \overline{V}$ iff $\pi(g, h, u) \in \overline{G}_M^{\geq 0}$).

The next step of the proof is to define for $\alpha \in \Phi$, $a \in A$ a partial function $T_\alpha(aX^{-1}) \colon V \not\to V$.
This function is defined for those triples $(g, h, u)$ for which $\pi(g, h, u) \in P_\alpha(*) \subseteq \overline{G}_M^{\geq 0}$.
If $\pi(g, h, u) \in P_\alpha(m)$ for some $m \in M$, then $T_\alpha(aX^{-1})$ is given by the following identity:
\[ T_\alpha(aX^{-1}) (g, h, u) = \left( x_\alpha(aX^{-1})\cdot g ,\
                                         h \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right),\ 
                                         u \cdot (1 + am)\right).\]
It is easy to verify that $\pi(T_\alpha(aX^{-1}) (g, h, u)) = S_\alpha(a, \pi(g, h, u)).$

\begin{lemma} $T_\alpha(aX^{-1})$ descends to a well-defined total function $T_\alpha(aX^{-1}) \colon \overline{V} \to \overline{V}$. \end{lemma}
\begin{proof}
 First of all, let us show that the resulting function is total. 
 We need to show that for every $(g, h\overline{G}^0_M, u) \in \overline{V}$ we can find a representative $h' \in h\overline{G}^0_M$
 such that $\pi(g, h', u) \in P_\alpha(*)$. Set $h' = h \cdot ev_{X=0}(\pi(g, h, u))^{-1}$, then
  \[\pi(g, h', u) = g \cdot j_-(h) \cdot \{ X, u \} \cdot \left(ev_{X=0}(g \cdot j_-(h))\right)^{-1} \in Im(K(A[X], M[X]) \to \St(\Phi, A[X, X^{-1}])) \subseteq P_\alpha(*).\]

 Next, we have to show that the value of $T_\alpha(aX^{-1})$ is well-defined. Suppose $(g, h_1, u), (g, h_2, u) \in V$ are such that 
  both $\pi(g, h_1, u)$ and $\pi(g, h_2, u)$ lie in $P_\alpha(*)$. Consequently, $j_-(h_1 h_2^{-1}) \in P_\alpha(*)$.

\end{proof}
